Cryptographic assurance of secrecy and fairness in voting

### 2012-12-05 paper/paper.tex
Add \pv{} command as a shortcut for Pret a Voter.

% custom commands
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:} \emph{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\bterm}[1]{\textbf{\textit{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\super}[1]{\textsuperscript{#1}}
\newcommand{\sub}[1]{\textsubscript{#1}}

@@

  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems to replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
	how three popular verifable voting systems -- Scantegrity, Pr\^{e}t \`{a} Voter, and Helios --
	use cryptographic techniques to meet those goals.

@@

In this survey, we will study three of the most well-known solutions: the in-person voting systems
Scantegrity and Pr\^{e}t \`{a} Voter and the online voting system Helios.

@@

\section{Pr\^{e}t \`{a} Voter}

@@

Helios \cite{helios} -- unlike Scantegrity and Pr\^{e}t \`{a} Voter -- is an \emph{online} voting
system that attempts to meet many of the same goals (namely, verifiability).

@@

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
``mixnet.'' \todo{We should discuss re-encryption details, which are covered in the Helios paper.
Maybe we cover the details in the Pr\^{e}t \`{a} Voter discussion?}

>>>>

% custom commands
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:} \emph{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\bterm}[1]{\textbf{\textit{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\super}[1]{\textsuperscript{#1}}
\newcommand{\sub}[1]{\textsubscript{#1}}
\newcommand{\preta}{Pr\^{e}t \`{a}}
\newcommand{\pv}{\preta{} Voter}

@@

  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems to replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
	how three popular verifable voting systems -- Scantegrity, \pv{}, and Helios --
	use cryptographic techniques to meet those goals.

@@

In this survey, we will study three of the most well-known solutions: the in-person voting systems
Scantegrity and \pv{} and the online voting system Helios.

@@

\section{\pv{}}

@@

Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
system that attempts to meet many of the same goals (namely, verifiability).

@@

Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
``mixnet.'' \todo{We should discuss re-encryption details, which are covered in the Helios paper.
Maybe we cover the details in the \pv{} Voter discussion?}
